Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-27 talk/icooolps2011/paper.tex
old author block

\authorinfo{Carl Friedrich Bolz \and XXX}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany
           }
           {cfbolz@gmx.de \and XXX}

>>>>

\authorinfo{Carl Friedrich Bolz$^a$ \and Antonio Cuni$^a$ \and Maciej Fijałkowski$^b$ \and Michael Leuschel$^a$ \and \\
            Samuele Pedroni$^c$ \and Armin Rigo$^a$}
           {$^a$Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany

            $^b$merlinux GmbH, Hildesheim, Germany

            $^c$Open End, Göteborg, Sweden
           }
           {cfbolz@gmx.de \and anto.cuni@gmail.com \and fijal@merlinux.eu \and
           leuschel@cs.uni-duesseldorf.de \and samuele.pedroni@gmail.com \and arigo@tunes.org}
